Survivable Set Connectivity

### 2015-05-09 draft.tex
further changes to rackes trees

>>>>

Finally, we for an edge $e \in E_T$, we define $y_e$ as follows. The removal of $e$ from $T$ separates the tree into two connected components. Let $S$ be the set of vertices of $G$ mapped to by the leaves of one of the connected component, and so $V \setminus S$ is the set of vertices of $G$ mapped to by the leaves of the other connected component. Define $\delta(S)$ to be the set of edges in $E$ that cross from $S$ to $V \setminus S$. Then we set $y_e = \sum_{e' \in \delta(S)} x_e$.
